# Interactivity
The great thing with using HTML is that you can make your notes as interactive as you like. This section shows you a few ways of introducing interactivity to your notes, but the possibilities are endless. 

## Reveal Hidden Text
You can hide and unhide some text (e.g. hints or optional solutions) as in the following example.

:::example
Use the "&lt;details&gt;" and "&lt;summary&gt;" html tags to hide and reveal text interactively.

```{html}
<details>
  <summary>click to unhide</summary>
  Here is some hidden text.
</details>
```

<details>

<summary>click to unhide.</summary>

<br>

This is the text/image etc. that I want to hide.

$a+b$

```{r,fig.alt="A graph that shows...", fig.cap="A graph demonstrating..."}
x<-rnorm(100,mean=4,sd=2)
y<-x^{2}
plot(x,y,lwd=4,main="Mock plot")

```

</details>
:::


## Embedded Video

Please watch the video below to see how we have embedded this video from mediaspace.

If the link does not work then please use [this alternative link.](https://mediaspace.nottingham.ac.uk/media/How+to+get+the+embed+links/1_824b1mfn)


<iframe id="kaltura_player" src="https://cdnapisec.kaltura.com/p/1355621/sp/135562100/embedIframeJs/uiconf_id/13188771/partner_id/1355621?iframeembed=true&playerId=kaltura_player&entry_id=1_824b1mfn&flashvars[streamerType]=auto&amp;flashvars[localizationCode]=en&amp;flashvars[leadWithHTML5]=true&amp;flashvars[sideBarContainer.plugin]=true&amp;flashvars[sideBarContainer.position]=left&amp;flashvars[sideBarContainer.clickToClose]=true&amp;flashvars[chapters.plugin]=true&amp;flashvars[chapters.layout]=vertical&amp;flashvars[chapters.thumbnailRotator]=false&amp;flashvars[streamSelector.plugin]=true&amp;flashvars[EmbedPlayer.SpinnerTarget]=videoHolder&amp;flashvars[dualScreen.plugin]=true&amp;flashvars[hotspots.plugin]=1&amp;flashvars[Kaltura.addCrossoriginToIframe]=true&amp;&wid=1_zv4m2ht2" width="456" height="292" allowfullscreen webkitallowfullscreen mozAllowFullScreen allow="autoplay *; fullscreen *; encrypted-media *" sandbox="allow-forms allow-same-origin allow-scripts allow-top-navigation allow-pointer-lock allow-popups allow-modals allow-orientation-lock allow-popups-to-escape-sandbox allow-presentation allow-top-navigation-by-user-activation" frameborder="0" title="Kaltura Player"></iframe>

<br>


:::example
**How to use the template - Another video example**

Note to use all of this you will need some IDE and R to be installed on your machine. Then you just need to open the project in your IDE.

Then  just create a new .qmd file to add a new chapter and add it into `_quarto.yaml` for the order you want that chapter to appear.

A video below shows what to do in more detail. If the video does not work then please use [this alternative link.](https://mediaspace.nottingham.ac.uk/media/How+to+use+the+template/1_brjfqb44)

<iframe id="kaltura_player" src="https://cdnapisec.kaltura.com/p/1355621/sp/135562100/embedIframeJs/uiconf_id/13188771/partner_id/1355621?iframeembed=true&playerId=kaltura_player&entry_id=1_brjfqb44&flashvars[streamerType]=auto&amp;flashvars[localizationCode]=en&amp;flashvars[leadWithHTML5]=true&amp;flashvars[sideBarContainer.plugin]=true&amp;flashvars[sideBarContainer.position]=left&amp;flashvars[sideBarContainer.clickToClose]=true&amp;flashvars[chapters.plugin]=true&amp;flashvars[chapters.layout]=vertical&amp;flashvars[chapters.thumbnailRotator]=false&amp;flashvars[streamSelector.plugin]=true&amp;flashvars[EmbedPlayer.SpinnerTarget]=videoHolder&amp;flashvars[dualScreen.plugin]=true&amp;flashvars[hotspots.plugin]=1&amp;flashvars[Kaltura.addCrossoriginToIframe]=true&amp;&wid=1_0ldbkr81" width="456" height="292" allowfullscreen webkitallowfullscreen mozAllowFullScreen allow="autoplay *; fullscreen *; encrypted-media *" sandbox="allow-forms allow-same-origin allow-scripts allow-top-navigation allow-pointer-lock allow-popups allow-modals allow-orientation-lock allow-popups-to-escape-sandbox allow-presentation allow-top-navigation-by-user-activation" frameborder="0" title="Kaltura Player"></iframe>

:::





## Quizzes

### Xerte

:::tip
<br>
For Xerte, just paste the embed code. Example below. Note, if you have your settings on Xerte so that the file can only be viewed from Moodle, then the Xerte file will only show if the Rbookdown file is uploaded to Moodle.

:::

<br>


<iframe src="https://www.nottingham.ac.uk/toolkits/play_25775" width=100% height=600px frameborder="0" style="position:relative; top:0px; left:0px; z-index:0;"></iframe>


<br>

If the interactive slides above do not work then please access them using [this link.](https://www.nottingham.ac.uk/toolkits/play_25775)

### Itempool

:::tip
Here we use r commands to add in a URL.
:::
<br>


```{r,echo=FALSE}
knitr::include_url("https://itempool.com/lisamott/c/4GwLabABphe")
```
<br>


### Microsoft Forms

:::example

This one has been used by copying and pasting the embed code from the microsoft form share settings.
:::

<br>

<iframe width="640px" height="480px" src="https://forms.office.com/Pages/ResponsePage.aspx?id=7qe9Z4D970GskTWEGCkKHoE3SM27-A1CtrKSdWhwNZ9UNUtCWEpYRzZIUzJQWkdJNzlaUzRXVTM1Qy4u&embed=true" frameborder="0" marginwidth="0" marginheight="0" style="border: none; max-width:100%; max-height:100vh" allowfullscreen webkitallowfullscreen mozallowfullscreen msallowfullscreen> </iframe>

